\newcommand{\tabitem}{~~\llap{\textbullet}~~}

\section{Functional Requirements}
To reach the main goals of the \emph{Travlendar+} application we need to satisfy these functional requirements:

\begin{requirementList}
	\item The user will have to specify a residence at registration time. This home address can be updated lately, thus the Software will have to permit to modify it. 
   
	\item The application must send a reminder to the user 30 minutes before he should begin the trip. Moreover, the application has to verify if a Sharing-Based vehicle is effectively available, if actually it is a user preference.
    
    \item If there isn't a Sharing based travel service available, the application must give a feasible alternative travel solution to the user according to his preferences.
    
    \item If two or more user's tasks have an overlapping, which cannot be schedule in a feasible way, the Application asks to the user to choose the task he prefers to do.
    
    \item The Software will have to permit the user to specify when he wants to return home. Thus, the software should have a special task representing it.
    
    \item The application has to reschedule a day if the user adds, deletes or updates a task during the day.
    
    \item If the user wants to add, delete or update a task during the day, the Application gives a travel solution that may not respect the time constraints.
    
    \item If the user adds a task that isn't reachable within the given time, the \emph{Travlendar+} System sends a warning to the user. 
    
    \item Each task can be repeated a finite or infinite number of times. In particular, a task can be repeated:
    \begin{enumerate}[label={[}R 9.\arabic*{]}:]
    \item the same day of every week
    \item the same day of every month
    \item the same day of every year
    \item two or more days during a single week
    \end{enumerate}
    Thus, the application should take care of repeated tasks considering the same specific preferences as defined by the user when creating the task.
    
    \item The application should consider whether the user is using private vehicles or not throughout a day.
    \begin{enumerate}[label={[}R 10.\arabic*{]}:]
    \item The Software should not suggest to use a private vehicle if the user left his residence without it.
   
    \item The software should consider that if the user left home using a private vehicle, it will be necessary to return home using the same private vehicle.
    \end{enumerate}
    
    \item The Software should permit to add or modify either general preferences, which are always taken care of, or specific preferences, which applies on a single task.
    \begin{enumerate}[label={[}R 11.\arabic*{]}:]
    \item If a specific preference conflicts with a general preference, the software will have to consider the specific one, ignoring the general one.
    \end{enumerate}
    
    \item The application should allow the user to insert tasks which are time-variable during the week. Thus, the Software should take care of these tasks scheduling them in an appropriate way, choosing day and time.
    
    \item The application should permit the purchase of either public transport service or vehicle sharing services through the respective external applications.
    
    \item The application should show all user's schedule with different kind of visualization: by month, by week or by day.
    
    \item The application should permit the selection of a single task, in order to show the relative preferences and should give the possibility to change these ones.
    
    \item The system has to guarantee new user signing up with a proper sign up page. 
    
    \item The system, in order to choose the best travel solution for the user, has to consider two main parameters: cost and time of the travel. To keep this kind of information, the system uses this formula: \( y = a \cdot cost + b \cdot time\). Therefore, the system will minimize the \(y\) variable. If there is two kinds of travels which have the same \(y\) value, so the application will ask to the user.
    
    \item If public transport is a user's preference, the system has to suggest the best ticket available with respect to the user's tasks. 
    \begin{enumerate}[label={[}R 18.\arabic*{]}:]
    \item If the user has already a season ticket, then this information will be taken into account when scheduling new and old user's tasks.
    \end{enumerate}

\end{requirementList}

\section{Use Case Diagram and Scenarios description}
\input{SpecificRequirements/UseCase/login.tex}
\input{SpecificRequirements/UseCase/newTask.tex}
\input{SpecificRequirements/UseCase/modifyTask.tex}
\input{SpecificRequirements/UseCase/breakTask.tex}
\input{SpecificRequirements/UseCase/infoTransport.tex}
\input{SpecificRequirements/UseCase/buyService.tex}
\input{SpecificRequirements/UseCase/reminder.tex}
\input{SpecificRequirements/UseCase/publicTransportInfo.tex}
\input{SpecificRequirements/UseCase/maps.tex}