\section{Functional Requirements}
To reach the main goals of the \emph{Travlendar+} application we need to satisfy these functional requirements:

\begin{requirementList}
	\item the user will have to specify a residence or home address at registration time. this home address can be updated lately, thus the Software will have to permit to modify it. 
   
	\item The application must send a reminder to the user 30 minutes before he should begin the trip.
    
    \item 10 minutes before the user starts his trip, the System must evaluate if a Sharing based travel service is effectively available, if actually is a user preference
    
    \item If there isn't a Sharing based travel service available, the application must give a feasible alternative travel solution to the user according to his preferences
    
    \item \textcolor{blue}{The Application has a 10 minutes time tolerance to avoid several delays} 
    
    \item If two or more user's tasks have an overlapping, which cannot be schedule in a feasible way, the Application asks to the user to choose the task he prefers to do
    
    \item the Software will have to permit the user to specify when he wants to return home. thus, the software should have a special task representing it. 
    
    \item The application has to reschedule a day if the user adds, deletes or updates a task during the day
    
    \item If the user wants to add, delete or update a task during the day, the Application gives a travel solution that may not respect the time constraints
    \item each task can be repeated a finite or infinite number of times. In particular, a task can be repeated:
    \begin{enumerate}[label={[}R 10.\arabic*{]}:]
    \item the same day of every week
    \item the same day of every month
    \item the same day of every year
    \item two or more days during a single week
    \end{enumerate}
    thus, the application should take care of repeated tasks considering the same specific preferences as defined by the user when creating the task.
    
    \item the application should consider whether the user is using private vehicles or not throughout a day. 
    \begin{enumerate}[label={[}R 11.\arabic*{]}:]
    \item the Software should not suggest to use a private vehicle if the user left his residence without it.
   
    \item the software should consider that if the user left home using a private vehicle, it will be necessary to return home using the same private vehicle.
    \end{enumerate} 
    \item cosa succede se un utente cerca di inserire un task in un time slot già occupato da un task fisso? da un task variabile "labile"? da un task variabile "importante" ? proposta rescheduling altro giorno ?
    
    \item the Software should permit to add or modify either general preferences, which are always taken care of, or specific preferences, which applies on a single task.
    \begin{enumerate}[label={[}R 13.\arabic*{]}:]
    \item if a specific preference conflicts with a general preference, the software will have to consider the specific one, ignoring the general one.
    \end{enumerate}
    
    \item the application should allow the user to insert tasks which are time-variable during the week. thus, the Software should take care of these tasks scheduling them in an appropriate way, choosing day and time.
    
    \item The application should permit the purchase of either public transport service or vehicle sharing services through the respective external application
    
    \item The application should show all user's schedule with different kind of visualization: by month, by week or by day
    
    \item The application should permit the selection of a single task, in order to show the relative preferences and should give the possibility to change these ones.
    
    \item The system has to guarantee new user signing up with a proper sign up page   
    
    \item If public transport is a user's preference, the system has to suggest the best ticket available with respect to the user's tasks, in order to minimize the public transport expense
    
    \item when adding a new fixed-time task, the Software will have to recalculate all the variable tasks in order to improve the schedule efficiency in terms of time spent traveling.
    
    \item 
\end{requirementList}