\section{Document Structure}
The \emph{Design Document} is devoted to explain, with a good level of detail, the chosen architecture to develop easily the entire system. So, the document is divided into seven chapters, each one with the intent to explain a view on the \emph{Travlendar+} System.

\begin{enumerate}

    \item Introduction: chapter devoted to describe the general purpose of both the document and the \emph{Travlendar+} application
    
    \item Architectural Design: chapter devoted to show the architectural chosen for \emph{Travlendar+}, the main physical components that will be used in the development phase. Moreover this section tries to explain the main modules used in each component and in each layer of the application.
    
    \item Algorithm Design: chapter used to explain, in a general form, the main algorithmic part of the \emph{Travlendar+} system, that is the explanation of the schedule algorithm used to construct the user's calendar.
    
    \item User Interface Design: chapter devoted to explain the main user interfaces used in the client layer, to handle properly the user's input and to show information to him.
    
    \item Requirements Traceability: section used to describe each application component with respect to the functional requirements which is satisfied by them.
    
    \item Implementation, Integration \& Test Plan: section used to describe the plan used when each component will be develop and how it will be integrated with the others components to simplify the testing.
    
    \item Effort Spent: chapter devoted to explain how the \emph{Travlendar+} team has worked, on which part of the document and how many hours each team component has spent in the creation of the document.
\end{enumerate}